On $2$-systoles of congruence quotients of $\mathrm{SL}_3$.

### 2024-04-01 systoles-SL3.tex
small changes

The observation that comes next is that the sequence of Lucas primes is very sparse. It is conjectured that there are infinitely many of them but even this is not known. In any respect, it is not hard to see that the number of Lucas primes less or equal than $N$ grows at most as fast as $O(\frac{1}{\log\log N})$. From a more general point of view we are interested in the order of the generators of $Z_{\SL}(\tilde A)$ mod $p$. One of the generators can be chosen as $\tilde{A}$ and is equal one mod $p$. We are left with the other generator.  This can sometimes have very small order compared to $p$, like in the case with the Lucas primes considered in Proposition~\ref{prop:lucas}. However, in most of the cases the order will be $~p$ which implies that the index of the centralizer will be also of order $p$.

>>>>

The observation that comes next is that the sequence of Lucas primes is very sparse. It is conjectured that there are infinitely many of them but even this is not known. In any respect, it is not hard to see that the number of Lucas primes less or equal than $N$ grows at most as fast as $O(\frac{\log\log N}{N})$. From a more general point of view we are interested in the order of the generators of $Z_{\SL}(\tilde A)$ mod $p$. One of the generators can be chosen as $\tilde{A}$ and is equal to one mod $p$. We are left with the other generator.  This can sometimes have very small order compared to $p$, like in the case with the Lucas primes considered in Proposition~\ref{prop:lucas}. However, in most of the cases the order will be $\sim p$ which implies that the index of the centralizer will be also of order $p$.
